The Splashback Radius of Planck-SZ clusters

### 2019-03-06 Paper_v2/RSP_paper_new.tex
changes in cornerplot
Corrections regarding proof of paper

\begin{figure*}
    \includegraphics[width= \textwidth]{corner215.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional
form in Equation~\ref{eq:model} for the PS 21.5 sample.
}
   \label{fig:corner_21.5}
\end{figure*}

@@

While this work was in preparation, we became aware of a related study
by Shin et al. (2018). Our results are complementary to theirs given
the different data samples and cluster catalogs.

>>>>

\begin{figure*}
    \includegraphics[width= \textwidth]{corner215.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional form in
Equation~\ref{eq:model} for the PS 21.5 sample. The dark and light magenta
contours represent the 68\% and 95\% confidence regions for the posterior
distribution of our parameters.
}
   \label{fig:corner_21.5}
\end{figure*}

@@

While this work was in preparation, we became aware of a related study
namely, \citet{shin2018des}. Our results are complementary to theirs given
the different data samples and cluster catalogs.
